City traffic, IoT and Blockchain technologies

### 2020-11-05 thesis/report2.tex
One more paragraph.

    This chapter is aiming to lay the ground on how we intend to bring the city traffic infrastructure from previous chapter and its needs into a blockchain technology. The two worlds, two very different paradigms, can be bridged together: IoT and Blockchain. The traffic of a city is an inherent IoT application. The actors, regardless of their type (cars, bikes, pedestrians), might have limited power consumption, might have intermittent internet conectivity and can be offline for long periods of time. Those constraints led to design an IoT solution for their communications. On the other side a Blockchain technology has needs which, at first sight, are in contrast with what an IoT device can do: proof of work is the first reason as it requires a great amount of power. Then the continuous online presence is needed, to participate in the blockchain network and stay up to date. Last, but not the least, the smart contracts nature of each Blockchain requires a different paradigm, a shift in how business logic are written. This comes with its own set of opportunities and limitations. To bring those areas together gaps must be identified in detail and bridges must be built over them. The target is to discuss those areas for two blockchains networks: Ethereum 2.0 and IOTA.

\section{Introduction}
\label{sec:sec}

@@

    What are the roles of smart contracts, though? Ever since the blockchain gained wider adoption the insufficiency of Bitcoin, first one of its kind and still the most successfull, has been an obstacle for implementing other types of transactions than the simple money transfer. Therefore other blockchain have started to be designed from the ground up to allow more complex logic. Examples are plenty: decentralized voting, assets transfer and ownership, etc.

\section{Proof of Work and Proof of Stake}
\label{sec:PoWandPoS}

% good behavior

@@

>>>>

    This chapter is aiming to lay the ground on how we intend to bring the city traffic infrastructure from previous chapter and its needs into a blockchain technology. The two worlds, two very different paradigms, can be bridged together: IoT and Blockchain. The traffic of a city is an inherent IoT application. The actors, regardless of their type (cars, bikes, pedestrians), might have limited power consumption, might have intermittent internet conectivity and can be offline for long periods of time. Those constraints led to design an IoT solution for their communications. On the other side, a Blockchain technology has needs which, at first sight, are in contrast with what an IoT device can do: proof of work is the first reason as it requires a great amount of power. Then the continuous online presence is needed, to participate in the blockchain network and stay up to date. Last, but not the least, the smart contracts nature of each Blockchain requires a different paradigm, a shift in how business logic are written. This comes with its own set of opportunities and limitations. To bring those areas together gaps must be identified in detail and bridges must be built over them. The target is to discuss those areas for two blockchains networks: Ethereum 2.0 and IOTA. Section \ref{sec:GapsBridges} will go into more detail.s

\section{Contents}
\label{sec:Contents}

@@

    What are the roles of smart contracts, though? Ever since the blockchain gained wider adoption the insufficiency of Bitcoin, first one of its kind and still the most successfull, has been an obstacle for implementing other types of transactions than the simple money transfer. Therefore other blockchain have started to be designed from the ground up to allow more complex logic. Examples are plenty: decentralized voting, assets transfer and ownership, etc. Ethereum is the most popular offering with a smart contracts (see section \ref{sec:EthereumNature}). IOTA is another one and is tailored for the IoT world.

    % some papers from 'papers 2' folder can be added here

% \section{Proof of Work and Proof of Stake}
% \label{sec:PoWandPoS}

    % some other papers from 'papers 2' folder

@@

    \paragraph{Serverless} We found out, already, that there is no central server into the sight of a blockchain or a distributed ledger technology. Therefore, our solution designed in chapter one, will need to undergo drastic modifications. There was already o similar idea which could help us on this matter, proposed by \cite{ApproachesToFrontEnd}. The frontend side will remain the actor's interaction with the user. An example can be an Android application running on the phone or an Android application running on a car's dashboard. The backend might have different configurations:

    \begin{itemize}
        \item Backend is running on the same machine with the frontend. For a mobile phone it might not be a good idea if the resources needed for it will drain batteries and consume data plans. For an application running on a car's dashboard, this can be an option.
        \item Backend is running on other machine than the one where the frontend is running. It can be a user's machine, running somwhere at home or in the cloud or it can be a paid one, a Software as a Service offering, run by a third party on behalf of the user. The core principle is that heavy computations, if necessary for Ethereum, for example, are handed over to a more powerful system.
        \item Backend is not running at all anywhere. Instead, all the interactions an actor need are sent to miners of a Blockchain. Miners will be responsible for gathering data, formulating responses and sending answers back to the users. All the interactions may be recorded on the ledger. The frontend will get its data from the ledger as soon as a miner adds it and is validated by the network.
    \end{itemize}

    \paragraph{Data on ledger} Having so many interactions between an actor's need and the ledger, there is the legitimate question of which data should be recorded forever on the ledger and which should not.

    \paragraph{Miners' decisions} The miner will decide the path the actor will travel

    \paragraph{Local ledgers} Coordinators, local 'servers' might exist for each city or region

    \paragraph{Actor role} What is an actor's role on the blockchain

    \paragraph{Third party observers} Participants on the network, only for observing
